---
title: "lab1"
author: "Zhidkov Georgy"
format: 
    md:
        output-file: README.md
---

## 1. Basic Building Blocks

In its simplest form, R can be used as an interactive calculator. Type 5 + 7 and press Enter.

```{r}
5 + 7
```

To assign the result of 5 + 7 to a new variable called x, you type x \<- 5 + 7. This can be read as 'x gets 5 plus 7'. Give it a try now. To view the contents of the variable x, just type x and press Enter. Try it now.

```{r}
x <- 5 + 7
x
```

Now, store the result of x - 3 in a new variable called y. What is the value of y? Type y to find out.

```{r}
y <- x - 3
y
```

The easiest way to create a vector is with the c() function, which stands for 'concatenate' or 'combine'. To create a vector containing the numbers 1.1, 9, and 3.14, type c(1.1, 9, 3.14). Try it now and store the result in a variable called z.

```{r}
z <- c(1.1, 9, 3.14)
z
```

Type ?c and press Enter. This will bring up the help file for the c() function. Type z to view its contents. Notice that there are no commas separating the values in the output.

```{r}
?c
```

You can combine vectors to make a new vector. Create a new vector that contains z, 555, then z again in that order. Don't assign this vector to a new variable, so that we can just see the result immediately.

```{r}
c(z, 555, z)
```

Numeric vectors can be used in arithmetic expressions. Type the following to see what happens: z \* 2 + 100.

```{r}
z * 2 + 100
```

Take the square root of z - 1 and assign it to a new variable called my_sqrt.

```{r}
my_sqrt <- sqrt(z - 1)
my_sqrt
```

Now, create a new variable called my_div that gets the value of z divided by my_sqrt.

```{r}
my_div <- z / my_sqrt
my_div
```

To see another example of how this vector 'recycling' works, try adding c(1, 2, 3, 4) and c(0, 10). Don't worry about saving the result in a new variable.

```{r}
c(1, 2, 3, 4) + c(0, 10)
```

Try c(1, 2, 3, 4) + c(0, 10, 100) for an example.

```{r}
c(1, 2, 3, 4) + c(0, 10, 100)
```

In many programming environments, the up arrow will cycle through previous commands. Try hitting the up arrow on your keyboard until you get to this command (z \* 2 + 100), then change 100 to 1000 and hit Enter. If the up arrow doesn't work for you, just type the corrected command.

```{r}
z * 2 + 1000
```

## 2. Workspace and Files

